Simple connectome inference from partial correlation statistics in calcium imaging

### 2014-06-20 article.tex
add a note

@@

\begin{figure}[bth]
\centering
\subfigure[]{\includegraphics[width=0.45\textwidth]{images/curve_roc} \label{fig:roc_curve}}
\subfigure[]{\includegraphics[width=0.45\textwidth]{images/curve_pr} \label{fig:pr_curve}}
\caption{The weighted average of partial correlation matrix, winning approach
         of the challenge, yields better than AUROC and AUPRC than all
         other state-of-the-art methods. (parameters: $\tau=0.11$, partial
         correlation used filer $f_1$).}
\label{fig:curves}
\end{figure}

@@

@@

\subsection*{Area under the ROC curve is a poor metric for network inference}

>>>>

\textcolor{red}{AJ: It's not clear on which datset we focus on}

@@

@@

\begin{figure}[bth]
\centering
\subfigure[]{\includegraphics[width=0.45\textwidth]{images/curve_roc} \label{fig:roc_curve}}
\subfigure[]{\includegraphics[width=0.45\textwidth]{images/curve_pr} \label{fig:pr_curve}}
\caption{The weighted average of partial correlation matrix, winning approach
         of the challenge, yields better than AUROC and AUPRC than all
         other state-of-the-art methods. (parameters: $\tau=0.11$ except for
         averaging method, partial correlation used filer $f_1$).}
\label{fig:curves}
\end{figure}

@@

\subsection*{Area under the ROC curve a poor metric for network inference}
